---
date: '`r paste0("Report created at: ", format(Sys.time(),"%A, %B %d, %Y %H:%M:%S"))`'
output:
  flexdashboard::flex_dashboard:
    orientation: columns
    storyboard: false
    logo: www/logo-icon.png
    self_contained: true
params: 
  calc_backtest: NA
  set_title: NA
---

---
title: `r params$set_title`
---

```{r setup, include=FALSE}
library(flexdashboard)
library(knitr)
library(gt)
library(ggplot2)
```
<script>
  $('.navbar-logo').wrap('<a href="https://www.envisionrisk.com" target=_blank>');
</script>


<style>
  .navbar, [data-toggle=tab], .navbar-brand  {   background-color:#AEC0C9;   border-color:black;   color:white; }
  
  .navbar-logo img {
    position: absolute;
    right: 0px;
  }
  
  .navbar-inverse .navbar-nav > li > a:hover,
  .navbar-inverse .navbar-nav > li > a:focus {
    background-color: #27647B;
      color: white;
  }
  .navbar-inverse .navbar-nav > .active > a,
  .navbar-inverse .navbar-nav > .active > a:hover,
  .navbar-inverse .navbar-nav > .active > a:focus {
    color: white;
    background-color: #27647B;
  }
  .navbar-inverse .navbar-toggle:hover,
  .navbar-inverse .navbar-toggle:focus {
    background-color: #27647B;
  }
  .navbar-inverse .navbar-collapse,
  .navbar-inverse .navbar-form {
    border-color: #27647B;
  }
</style>

## Column {data-width=10%}

#### **Assumptions**

### Base Currency {data-height=15%}
```{r}
color_classic_trustworthy <- c("#CA3542", "#27647B", "#849FAD", "#AEC0C9", "#57575F")  
flexdashboard::valueBox(params$calc_backtest$Input$base_cur, "Base Currency", icon = "fas fa-money-bill", color = color_classic_trustworthy[3])
```

### Signif Value {data-height=15%}
```{r}
    flexdashboard::valueBox(paste(round(100*params$calc_backtest$Input$signif_level, 1), "%", sep=""), "Significance Level", icon = "fas fa-crosshairs", color = color_classic_trustworthy[5])
```

Column {data-width=55%}
-----------------------------------------------------------------------

### Input data for the the backtest

```{r, fig.width=10, fig.height=8}
  suppressMessages(envrsk_backtest_dashboard_ts(params$calc_backtest$Input$backtestdata,
                                                params$calc_backtest$Input$base_cur))
```

> The figure shows daily Value-at-risk & Expected Shortfall risk predictions together with daily Profit/Loss observations. The "red" dots highlights the Value-at-Risk-events where the Profit/Loss is worse (more negetive) than predicted by Value-at-Risk. 

Column {data-width=25%}
-----------------------------------------------------------------------

### Summary of the backtest {data-height=60%}

```{r, fig.width=6, fig.height=8}
  suppressMessages(envrsk_backtest_dashboard_summary_risk(params$calc_backtest$Output))
```

> The summary of the backtest is created based on the daily input-values 
for Profit/Loss, Value-at-Risk and Expected-Shortfall. The p-value can 
be interpretated as a likelihood of observing an even worse outcome 
than observed (i.e. more frequent loss-events for Value-at-Risk and 
more severe losses for Expected-Shortfall) under the assumption that the 
model is accurate (the null hypothesis). In case where the p-value is low 
this is used as evidence against the hypothesis and hence conclude that 
the model show signs of not being accurate.   

Column {data-width=10%}
-----------------------------------------------------------------------

### P-value Interpretation 

```{r}
  suppressMessages(envrsk_backtest_dashboard_p_value_interpretation_table())
```

> The interpretation of 'p-value < 10%' is that the p-value is higher
than 5% but lower than 10%. The same rationale for the rest of the p-values.
We dont calculate an exact p-value, but only calculte it for certain cutoff 
values.